Comparative vaccine effectiveness of ChAdOx1 versus BNT162b2 in Health and Social Care workers in England

### 2021-09-01 analysis/report/draft-manuscript.Rmd
typo

```{r comp,echo=FALSE, message=FALSE, warnings=FALSE, out.width='90%', fig.height=8, results='asis'}
patchwork::wrap_plots(plot_cmlinc, plot_riskdiff, plot_hazard, ncol=1)
```

>>>>

```{r comp,echo=FALSE, message=FALSE, warning=FALSE, out.width='90%', fig.height=8, results='asis'}
patchwork::wrap_plots(plot_cmlinc, plot_riskdiff, plot_hazard, ncol=1)
```
